\documentclass[11pt]{article}

\usepackage{mathpazo}

\usepackage[margin=1in]{geometry}

\usepackage{hyperref}

\usepackage[defaultsans]{cantarell}
\usepackage[T1]{fontenc}

\usepackage[para]{footmisc}

\usepackage[small,compact]{titlesec}
\titlespacing{\subsection}{0pt}{*2}{*0.125}
\titleformat*{\subsection}{\sffamily\bfseries}
\titleformat*{\section}{\sffamily\bfseries}

\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\footnotesize \sf Software in Astronomy \& Astrophysics}
\lhead{}

\newenvironment{squishlist}
  {\begin{itemize}
    % set spacing between items
    \addtolength{\itemsep}{-0.33\baselineskip}
    % set spacing between lines
    %\addtolength{\baselineskip}{-0.25\baselineskip}
   }
  { \end{itemize} }


\usepackage{tcolorbox}

\begin{document}

\thispagestyle{plain}

\mbox{ }\vspace{-0.7in}

\begin{center}
{\Large \sffamily \bfseries Software in Astronomy \& Astrophysics:\\The Importance and Need for Sustained Funding} \\
{
everyone!
}
\end{center}

\begin{tcolorbox}
{\sffamily \bfseries Executive Summary:} 
\end{tcolorbox}

\section{Introduction}

Astronomy depends on computation---for simulation, data analysis, modeling, ...

Open source software has played a large role in astronomy for more than
25 years.  (both simulation codes and observational reduction / pipelines)

Computational science is of growing importance.


\section{Software Development}

Software is complex

architectures change

long term funding for software is necessary to develop and maintain
codes---analogous to instrument design

no mainstream {\em professional software track} analogous to telescope
operators or instrument builders.


\subsection{Benefits to the Developer}

citations


\subsection{Costs to the Developer}

Code development is not always recognized in job-searches, promotion, ...



\section{Supporting Software}

Software development is supported via a variety of mechanisms:

grassroots collaboration

single-investigator grants

NSF SSI, TCAN

DOE SciDAC, NNSA, ECP, ...

NumFocus

DOE does longterm support of software (e.g., linear solver packages).
NSF software support is much shorter term---hard to keep a development
team together.

What about something analogous to NSF MURI/MRI?


\section{Community Codes}

Once codes become large enough and adopted by the community, funds are
needed for maintainence as well as new developments.

For HPC codes, changing architectures (many-core, GPUs, ...) require rewriting
algorithms.







\end{document}
